### 2019-02-22 sections/intuition.tex
add todo
extended intuition of breakfast example

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink. \makeFood. makeDrink <&> makeFood in
  makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? haveBreakfast
\end{TASK}

@@

>>>>

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink. \makeFood. makeDrink <&> makeFood in
  makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? enjoyBreakfast
\end{TASK}

@@

The way the combinators are defined matches real life closely.
When we want to have breakfast, we have to complete several other tasks first before we can do so.
We decide what we want to have and then prepare it.
We can prepare the different items we have for breakfast in parallel, but not at the same time.
For example, it is impossible to scramble eggs, and put on the kettle for tea simultaneously.
Instead, what is meant by parallel is that the order in which we do tasks and the smaller tasks that they are composed of, does not matter.
Then finally, only when every item we want to have for breakfast is ready, can we sit down and enjoy it.
\end{example}
